Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
section 4.1.2

The \texttt{frag} benchmark takes the most time of any benchmark. When a region of the
address space is being expanded, the kernel is forced to unmap it and map a new
area elsewhere in the address space. This operation needs creation of a new
\texttt{vm\_area\_struct}.  The kernel also must search through the red-black
tree, though it never finds a node which can be expanded to include the new
mapping. Then, an insertion on the tree is needed, possibly including
rebalancing. Moreover, the existing \texttt{ vm\_area\_struct} needs to be
removed from the tree.

The \texttt{stride} workload is very similar to \texttt{frag} because it will also force the
kernel to always create a new structure and insert it into the tree after
traversing the tree first. However, it does not need to delete an existing
structure, which causes it to be faster than the \texttt{frag} benchmark.

>>>>

The \texttt{frag} benchmark takes the most time of any benchmark. When a region
of the address space is being expanded, the kernel is forced to unmap it and
map a new area elsewhere in the address space.  The kernel must search through
the red-black tree, though it never finds a node which can be expanded to
include the new mapping.  Then, the existing \texttt{ vm\_area\_struct} needs
to be removed from the tree.  Finally, a new \texttt{vm\_area\_struct} is
created and inserted into the tree.

The \texttt{stride} workload is very similar to \texttt{frag} because it will also force the
kernel to always create a new structure and insert it after
searching the tree. However, it does not need to delete an existing
structure, which causes it to be faster than the \texttt{frag} benchmark.
